\documentclass{article}
\usepackage[utf8]{inputenc}



\begin{document}
\large{Adventure Story} \\ \\
This is a story about four friends who took a walk in the park. One of the four got lost, so the remaining three (Alice, Bob, and Candice) all decided that they would split up and look for their lost friend, Diego. This story took place in 1974 so nobody had a cell phone on their person.\\
Diego has always been suspect so it did not come as a surprise to anyone that he found himself in a situation in which a search party was looking for him. Nevertheless, his friends had to come up with a strategy in order to find him. Alice decided to check the lake that had ducks because she knows of Diego's obsession with ducks, Bob was going to check the open field area that contained all of the people tanning because he knew Diego would never refuse a chance to tan, and finally, Candice was going to check the coffee shop that was in the park because she knew that Diego is addicted to caffeine.\\
While Alice was looking for Diego at the lake, she noticed that there was one particularly large duck, roughly the size of an ostrich. This duck was so large, it attracted the attention of almost everyone in the vicinity. Alice when to investigate the crowd but she was unsuccessful in finding Diego in the crowd. \\
Although Bob went to search for Diego in the open field, he took this opportunity to lay down in the sun himself because he felt extremely self conscience about his pale skin. This was an unfortunate decision because while Bob was laying down, he became a little bit too comfortable and fell asleep under the sun for two hours. This resulted in poor Bob to be sun-burnt as well as not being able to locate Diego.\\
Candice was confident that she would find Diego somewhere near the coffee stand for two reasons. One because Diego was highly addicted to caffeine and, and two because this coffee stand was one of the best in the northern-eastern corner of the United States. People would travel from all over the world to taste some of this coffee so it felt only right that she was going to find Diego in line. However to her dismay, Diego was not anywhere to be found and she was left distraught in her findings.\\
After what felt like months of searching for Diego, the three friends eventually burned out and decided to meet up at the center of the park in order to discuss their findings. When they arrived ready to share their stories, they found that their friend Diego has been at the center of the park all along. When they asked him, "Where have you been Diego? We've been looking for you!" His only response was, "I've been around." This describes Diego's personality best because he was so vague and to the point.
\end{document}
